Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales

### 2015-07-14 paper.tex
Sanity checks for Takahashi 2010 Fig 11

\section{Results}

Figure \ref{AllData} shows values of solar wind averages and mass density used in this study. We will briefly compare our results to other published results to verify our methods and handling of data.

\subsection{Previous Results}
Figure \ref{DailyAverages} show that the trends observed by \cite{Takahashi2010} for one day averages only seems to hold true for the one-day averaged data, and only after the $F_{10.7}$ dependence is removed. The correlation seen between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$ isn't quite as good in this data as in \cite{Takahashi2010}, but shows the same trend as seen in Figure \ref{ccplot}.

@@

\section{Appendix}
\subsection{Bias}

@@

While the GOES Satellites tend to keep an average geostationary distance of around $L=6.8R_E$ shown in \cite{Takahashi2010}, the actual plasmapause location varies significantly , as shown in \cite{OBrien2003}. This means that during periods of large $D_{st}$ the plasmapause may be far from the point of measurement of $\rho_{eq}$ creating a discord in the correlation. \cite{Gallagher2000} provides a model for $\rho_{eq}$ at a range of L-shells and a brief discussion of the elemental contributions.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.5]{paperfigures/stormavs-dst-day.eps}
\includegraphics[scale=0.5]{paperfigures/stormavs-dst-day-50.eps}
\caption{One-day averaged $D_{st}$ storms at thresholds of $-40nT$ and $-50nT$}
\label{DailyAverages}
\end{figure}
\clearpage

@@

>>>>

\section{Results}
Figure \ref{AllData} shows values of solar wind averages and mass density used in this study. We will briefly compare our results to other published results to verify our methods and handling of data.

\subsection{Previous Results}
Figure \ref{DailyAverages} show that the trends observed by \cite{Takahashi2010} for one day averages only seems to hold true for the one-day averaged data. Namely that a drop in median daily $D_{st}$ between 1989 and 1991 coincides with a significant spike in $\rho_{eq}$. The correlation seen between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$ isn't quite as good in this data as in \cite{Takahashi2010}, but shows the same trend as seen in Figure \ref{ccplot}.

@@

\section{Appendix}
\subsection{Bias}
In an attempt to reproduce Figure 11 from \cite{Takahashi2010}, an ambiguity in data-handling was found. It is unknown how they got from hourly $\rho_{eq}$ to daily medians, whether in one step or two steps, so attempts were made to reproduce all possibilities and compare in order to find a data-handling method with the least bias. These attempts are shown in Figure \ref{blockmedian}. This also shows the effect of only considering events with a minimum before noon. All show a similar spike in $\rho_{eq}$ at the time of $D_{st}$ minimum, though none quite reproduce the exact values seen in \cite{Takahashi2010}. Figure \ref{allstorms} shows where the median falls for all of the found storms during that period, as a sanity check for why the prior work would get median values nearing $30 amu/cm^3$.

@@

While the GOES Satellites tend to keep an average geostationary distance of around $L=6.8R_E$ shown in \cite{Takahashi2010}, the actual plasmapause location varies significantly, as shown in \cite{OBrien2003}. This means that during periods of large $D_{st}$ the plasmapause may be far from the point of measurement of $\rho_{eq}$ creating a discord in the correlation. \cite{Gallagher2000} provides a model for $\rho_{eq}$ at a range of L-shells and a brief discussion of the elemental contributions.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-50-tak.eps}
\caption{(a) One-day medians of $D_{st}$ storms at a threshold of $-40nT$ and (b) verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991}
\label{DailyAverages}
\end{figure}
\clearpage

@@

\begin{figure}[htp]
\centering
\includegraphics[scale=0.75]{paperfigures/blockmedian.eps}
\includegraphics[scale=0.75]{paperfigures/blockmedian-prenoon.eps}
\caption{Comparing median values calculated as median of all 1-hour points in the 12 day block, and as the daily median of all hourly-mediated storms. (b) Same, but only storms starting between 0-12 UTC}
\label{blockmedian}
\end{figure}
\clearpage

\begin{figure}[htp]
\centering
\includegraphics[scale=0.9]{paperfigures/allstorms.eps}
\caption{Comparing all storms to their median and $1\sigma$ range}
\label{allstorms}
\end{figure}
\clearpage
